---
title: "Random Variables"
output: html_notebook
---

## Discrete Random Variables

### The Binomial Random Variable

```{r}
dbinom(c(1,3,5,7,9), 10, 0.5)
```

This output contains the Binomial probabilities of the values in the first argument. In order to obtain the probability of the event {X is odd} we should sum up these probabilities
```{r}
sum(dbinom(c(1,3,5,7,9), 10, 0.5))
```

```{r}
x <- 0:10
dbinom(x, 10, 0.5)
```

pbinom produces the cumulative proba- bility of the Binomial
```{r}
pbinom(x, 10, 0.5)
cumsum(dbinom(x, 10, 0.5))
```

```{r}
X.val <- 0:10
P.val <- dbinom(X.val, 10, 0.5)
EX <- sum(X.val*P.val)
EX
sum((X.val-EX)^2*P.val)
```

### The Poisson Random Variable

```{r}
x <- 0:10
dpois(x, 2)
```

```{r}
ppois(x, 2)
```

```{r}
X.val <- 0:10
P.val <- dpois(X.val, 2)
EX <- sum(X.val * P.val)
EX
```

```{r}
X.val <- 0:100
P.val <- dpois(X.val, 2)
EX <- sum(X.val * P.val)
EX
sum((X.val-EX)^2 * P.val)
```

## Continuous Random Variable

Uniform  
Exponential  

### The Uniform Random Variable

```{r}
dunif(0:10, 3, 7)
```

```{r}
dunif(4.73, 3, 7)
```

```{r}
punif(4.73, 3, 7)
```

```{r}
x <-seq(0, 10, length=1000)
den <- dunif(x, 3, 7)
plot(x, den)
```

```{r}
plot(x, den, type="l")
```

```{r}
cdf <- punif(x, 3,7)
plot(x, cdf, type = "l")
```

### The Exponential Random Variable

```{r}
pexp(6, 0.5) - pexp(2, 0.5)
```

