---
title: "The Normal Distribution"
output: html_notebook
---
The density of the Normal distribution can be computed with the aid of the function “dnorm”.
The cumulative probability can be computed with the function “pnorm”.

P(X ≤ 5) P(X ≤ 0)
```{r}
pnorm(5, 2,3) - pnorm(0, 2,3)
```

## The standard normal distribution

The standard normal distribution is a normal distribution of standardized values, which are called z-scores.
A z-score is the original measurement measured in units of the standard deviation from the expectation.
The calculation of the z-score emerges from the equation:
(0 =) x = μ + z · σ (= 2 + z · 3)

### computing percentiles

```{r}
# computes central 95% percent
# 97.5%-percentile
qnorm(0.975)
# 2.5%-percentile
qnorm(0.025)

```

lower and upper thresholds for the defining outliers
```{r}
qnorm(0.75) + 1.5*(qnorm(0.75)-qnorm(0.25))
qnorm(0.25) - 1.5*(qnorm(0.75)-qnorm(0.25))
```

## Continuity Corrections

without correction
```{r}
pbinom(6,30,0.3)
pnorm(6,30*0.3,sqrt(30*0.3*0.7))
```

with correction
```{r}
pnorm(6.5,30*0.3,sqrt(30*0.3*0.7))
```

